Development of a 3D display

### 2016-05-17 paper.tex
fixed siunitx

% Display SI units
\usepackage[separate-uncertainty=true, multi-part-units=single]{siunitx}

@@

Something I had in mind since the beginning of this project were animated images. The Teensy 3.1
has \SI{256}{\kilo\byte} of memory, which would fit 42 images of \SI{6}{\kilo\byte} each. This
corresponts to roughly a second of playback. In order to display longer animations, there are
several workarounds: Instead of showing one image that spans the entirety of the rotation, I can
instead only save an image that is 25 pixels and display it four times.

In order to get around the limit of flash memory, external storage would be necessary. Even with
only \SI{1}{\giga\byte}, I could save 166666 frames, thus removing any practical limit in terms of
playback time.

@@

Another possibility would be video games. Although the limited resolution and computing power
would make it difficult to run the newest games, 3D version of classics like Pong, Snake or a
simple platform game would be worth a shot.

>>>>

% Display SI units
\usepackage[separate-uncertainty=true, multi-part-units=single]{siunitx}
\sisetup{load-configurations = binary}

@@

Something I had in mind since the beginning of this project were animated images. The Teensy 3.1
has \SI{256}{kB} of memory, which would fit 42 images of \SI{6}{kB} each. This
corresponts to roughly a second of playback. In order to display longer animations, there are
several workarounds: Instead of showing one image that spans the entirety of the rotation, I can
instead only save an image that is 25 pixels and display it four times.

In order to get around the limit of flash memory, external storage would be necessary. Even with
only \SI{1}{GB}, I could save 166666 frames, thus removing any practical limit in terms of
playback time.

@@

Another possibility would be video games. Although the limited resolution and computing power
would make it difficult to run the newest games, 3D versions of classics like Pong, Snake or a
simple platform game would be worth a shot.
